Title Goes Here

### 2020-04-28 analysis/paper/paper.Rmd
added some descriptions

library(tidyr)
cv_plot_stage %>% 
pivot_longer(cols = -SPstage.Stage, names_to = "group") %>%
ggplot(aes(x = group, y = value, fill = as.factor(SPstage.Stage))) + 
geom_bar(stat="identity", position=position_dodge())

@@

```
=> We may need to delete this chunk since we made

@@

### three phases at once
library(patchwork)
call + ctwo + cthree + plot_layout(ncol=1)
```

>>>>

library(tidyr)
cv_plot_stage %>% 
pivot_longer(cols = -SPstage.Stage, names_to = "group") %>%
ggplot(aes(x = group, y = value, fill = as.factor(SPstage.Stage))) + 
geom_bar(stat="identity", position=position_dodge()) + labs(x="Attributes", fill= "Phase")

@@

```
=> We may need to delete this chunk since we made new plots below using corrr package and same dataset.

@@

### three phases at once
library(patchwork)
call + ctwo + cthree + plot_layout(ncol=1)
```
When it comes to the correlations between seven attributes, BL-ML, TW-MW, TL-TW, and TL-SL are relatively close to each other. There is no negative correlation among the attributes. Compared to the 2nd phase, in 3rd phase, correlations of SL with TW and MW, and TL with TWm SL, and MW get stronger. On the other hand, the correlation of TW-SW becomes weeker. Overall, the correlation between attributes became stronger from 2nd to 3rd phase.

Combined the two results of CV and correlation from 2nd to 3rd,

CV: lower in MW and TW, but higher in other 5 attribtues.

COR: stronger
